### 2012-02-05 sermons/Revelation1:1.tex
Sermon on Rev 1:1 done.

\documentclass[12pt]{article}
\newcommand{\BI}{\begin{itemize}}
\newcommand{\EI}{\end{itemize}}
\newcommand{\I}{\item}
\newcommand{\Q}[1]{\begin{quote} #1 \end{quote}}
\begin{document}
\part*{Revelation 1:1-3 --- The Revelation of Jesus Christ}
\tableofcontents
\BI
\section*{Notes}
\I  The point of this sermon is:
        \begin{quote} 
        You need to know and obey the Revelation of Jesus Christ.
        \end{quote}

@@

In this light, the goal of this sermon is to place a burden on the hearers 
    to know and become familiar with the contents of this book, 
    and to heed the commands given in it.

\section*{Introduction}
\section{The Subject of the Revelation of Jesus Christ}
\I The book of Revelation reveals Jesus Christ.
\subsection{He is God}
\I Rev 1:11 \Q{``I am the Alpha and the Omega, the First and the Last.''}
\I Rev 1:17 \Q{``Do not be afraid, I am the First and the Last.''}
\I Rev 22:13 \Q{``I am the Alpha and the Omega, the Beginning and the End, 
                the First and the Last.''}
\I Rev 1:13 \Q{\ldots and in the midst of the seven lampstands One 
                like the Son of Man, \ldots}
\I Rev 3:1, 5:6
            \Q{``These things says He who has the seven Spirits of God 
                and the seven stars: \ldots''}    
            \Q{And I looked, and behold, in the midst of the throne 
                and of the four living creatures, 
                and in the midst of the elders, 
                stood a Lamb as though it had been slain, 
                having seven horns and seven eyes, 
                which are the seven Spirits of God sent out into all the earth.}
\I Rev 3:14 \Q{``These things says the Amen, the Faithful and True Witness,
                the Beginning of the creation of God; \ldots}
\I Rev 22:16 \Q{``I, Jesus, have sent My angel to testify to you these things 
                in the churches, I am the Root and the Offspring of David, 
                the Bright and Morning Star.''}
\I Rev 1:16 \Q{\dots and His countenance was like the sun shining 
                in its strength.}

\subsection{He is the Savior}
\I Rev 1:5 \Q{To Him who loved us and washed us from our sins 
                in His own blood, \ldots}
\I Rev 1:18 \Q{I am He who lives, and was dead, and behold, 
                I am alive forevermore.}
\I Rev 5:6 \Q{And I looked, and behold, in the midst of the throne
                and of the four living creatures, and in the midst of the
                elders, stood a Lamb as though it had been slain, \ldots}
\I Rev 13:8 \Q{All who dwell on the earth will worship him [the beast], 
                whose names have not been written in the Book of Life
                of the Lamb who was slain from the foundation of the world.}
\I Rev 5:9 \Q{``You are worthy to take the scroll, \\
                And to open its seals; \\
                For You were slain, \\
                And have redeemed us to God by Your blood \\
                Out of every tribe and tongue and people and nation, \ldots''}
\I Rev 5:12 \Q{``Worthy is the Lamb who was slain \\
                To receive power and riches and wisdom, \\
                And strength and honor and glory and blessing!''}
\I Rev 5:13 \Q{``Blessing and honor and glory and power \\
                Be to Him who sits on the throne, \\
                And to the Lamb, forever and ever!''}
\I Rev 5:5 \Q{``Do not weep. Behold, the Lion of the tribe of Judah,
                the Root of David, has prevailed to open the scroll 
                and to loose its seven seals.''}
\I Rev 3:7 \Q{``He who has the key of David, He who opens and no one shuts, 
                and shuts and no one opens.''}
\I Rev 1:18 \Q{``And I have the keys of Hades and of Death.''}
\I Rev 19:7 \Q{``Let us be glad and rejoice and give Him glory,
                for the marriage of the Lamb has come,
                and His wife has made herself ready.''}
\I Rev 7:17 \Q{``for the Lamb who is in the midst of the throne 
                will shepherd them and lead them to living fountains of waters.
                And God will wipe away every tear from their eyes.''}
\I Rev 21:22-23 \Q{But I saw no temple in it, for the Lord God Almighty 
                and the Lamb are its temple. The city had no need 
                of the sun or of the moon to shine in it, 
                for the glory of God illuminated it. The Lamb is its light.}
\I Rev 22:1-2 \Q{And he showed me a pure river of water of life, 
                clear as crystal, proceeding from the throne of God 
                and of the Lamb. In the middle of its street, and on either
                of the river, was the tree of life, which bore twelve fruits,
                each tree yielding its fruit every month. 
                The leaves of the tree were for the healing of the nations.}
\I Rev 22:3-4 \Q{And there shall be no more curse, but the throne of God
                and of the Lamb shall be in it, and His servants shall 
                serve Him. They shall see His face, and His name shall be on
                their foreheads.}

\subsection{He is the conquering King}
\I Rev 1:7 \Q{Behold, He is coming with clouds, and every eye will see Him, 
                even they who pierced Him. And all the tribes of the earth
                will mourn because of Him. Even so, Amen.}
\I Rev 1:14-16 \Q{His head and hair were white like wool, as white as snow,
                and His eyes like a flame of fire; His feet were like brass, 
                as if refined in a furnace, and His voice as the sound of 
                many waters; He had in his right hand seven stars, 
                out of His mouth went a sharp two-edged sword, 
                and His countenance was like the sun shining in its strength.}
\I Rev 6:16-17 \Q{\ldots and said to the mountains and rocks, 
                ``Fall on us and hide us from the face of Him who sits on the
                throne and from the wrath of the Lamb! For the great day of His
                wrath has come, and who is able to stand?''}
\I Rev 14:14 \Q{Then I looked, and behold, a white cloud, and on the cloud
                sat One like the Son of Man, having on His head a golden crown, 
                and in His hand a sharp sickle.}
\I Rev 17:14 \Q{``These [ten kings and the beast] will make war with the Lamb, 
                and the Lamb will overcome them, for He is Lord of lords and
                King of kings; and those who are with Him are called, 
                chosen, and faithful.''}
\I Rev 19:11-16 \Q{Now I saw heaven opened, and behold, a white horse.
                And He who sat on Him was called Faithful and True,
                and in righteousness He judges and makes war.
                His eyes were like a flame of fire, and on His head were
                many crowns. He had a name written that no one knew except
                Himself. He was clothed with a robe dipped with blood,
                and His name is called The Word of God.
                And the armies of heaven, clothed in fine linen, white and
                clean, followed Him on white horses.
                Now out of His mouth goes a sharp sword, that with it He 
                should strike the nations. And He Himself will rule them 
                with a rod of iron. He Himself treads the winepress of the
                fierceness and wrath of Almighty God. And He has on His robe 
                and on His thigh a name written:
                \Q{KING OF KINGS \\ AND LORD OF LORDS.}}

\I Rev 20:15 \Q{And anyone not found written in the Book of Life was cast 
                into the lake of fire.}
            Note: we know this is the Lamb's Book of Life from Rev 13:8.

@@

\subsection{Things which must shortly take place}
\I \emph{Transition:} We must make Revelation an urgent, \#1 priority,
    because it informs us of the imminent.
\I If imminent back then, how much more so now!
\I Revelation has \emph{not} been fulfilled:
\BI \I We are not in the new heaven and the new earth.
    \I Death and Hades have not been thrown into the lake of fire.
    \I Sin has not been abolished.
    \I There still remains the final battle against Satan and the world.
    \I The final judgement of sinners and the righteous.
    \I Christ's evaluation of believers. \EI
\I These things are future, but not far off, they are future imminent.
\BI \I The Lord is not slow, He is merciful (2 Peter 3:19)
    \I Nothing is hard for Him, 
        but His judgement would have been far too much for you to bear! \EI
\I The Second Coming is unheralded, it comes without warning.
\BI \I Rev 22:7, 12 \Q{``Behold! I am coming quickly!''}
    \I Rev 16:15 \Q{``Behold! I am coming as a thief''} \EI
\I We must learn from the flood of Noah's time (Matt 24:38-39).
    \Q{``For as in the days before the flood, they were eating and drinking,
    marrying and giving in marriage, until the day that Noah entered
    the ark, and did not know until the flood came and took them all away,
    so also will the coming of the Son of Man be.''} 
\I We must be those who are prepared for His return 
    (Matt 25, parable of the virgins).
\I And we can start on this by reading, understanding, and obeying
    the Revelation of Jesus Christ.

\section{The Authority of the Revelation of Jesus Christ}
\subsection{The word of God}
\subsection{The testimony of Jesus Christ}
\subsection{All things that he saw}

\section{The Blessing of the Revelation of Jesus Christ}
\EI
\end{document}

>>>>

\documentclass[12pt]{article}
\newcommand{\BI}{\begin{itemize}}
\newcommand{\EI}{\end{itemize}}
\newcommand{\I}{\item}
\newcommand{\Q}[1]{\begin{quote} #1 \end{quote}}
\begin{document}
\part*{Revelation 1:1 --- 
        The Person and Purpose of the Revelation of Jesus Christ}
\tableofcontents
\BI
\section{Introduction}
\I  The point of this sermon is:
        \begin{quote} 
        You need to know and obey the Revelation of Jesus Christ.
        \end{quote}

@@

In this light, the goal of this sermon is to place a burden on the hearers 
    to know and become familiar with the contents of this book, 
    and to heed the commands given in it.
That they would be convinced that Revelation is critical to living a 
    victorious life in Christ Jesus.

Even beyond this, the goal is to show Jesus Christ and to call people 
    to faith and obedience in Him.

\I Envelope analogy

\section{The Person of the Revelation of Jesus Christ}
\I The book of Revelation reveals Jesus Christ.
\BI \I That is is His revelation (given to Him by God).
    \I That it is about Him (The disclosure, or unveiling, of Jesus Christ).
    \I He is who John saw.
    \I He is the One speaking to the Churches.
    \I He is the One who will end the world. \EI
\I  Reveltation gives us an exalted, and often unique, 
    understanding of who Jesus is.
\I Specifically, Revelation shows us that Jesus is God, the Savior, and
    the conquering King.

\subsection{He is God}
\I He is eternal, unchanging, and infinitely above all creation.
\BI \I Rev 1:11 \Q{``I am the Alpha and the Omega, the First and the Last.''}
    \I Rev 1:17 \Q{``Do not be afraid, I am the First and the Last.''}
    \I Rev 22:13 \Q{``I am the Alpha and the Omega, the Beginning and the End, 
                    the First and the Last.''} \EI
\I He directs and controls the Holy Spirit.
\BI \I Rev 3:1, 5:6
            \Q{``These things says He who has the seven Spirits of God 
                and the seven stars: \ldots''}    
            \Q{And I looked, and behold, in the midst of the throne 
                and of the four living creatures, 
                and in the midst of the elders, 
                stood a Lamb as though it had been slain, 
                having seven horns and seven eyes, 
                which are the seven Spirits of God sent out into all the earth.}
\EI
\I He is the Creator.
\BI \I Rev 3:14 \Q{``These things says the Amen, the Faithful and True Witness,
                    the Beginning of the creation of God; \ldots} \EI
\I He is the Light.
\BI \I Rev 22:16 \Q{``I, Jesus, have sent My angel to testify to you these 
                things in the churches, I am the Root and the Offspring of 
                David, the Bright and Morning Star.''}
    \I Rev 1:16 \Q{\dots and His countenance was like the sun shining 
                    in its strength.} \EI

\subsection{He is the Savior}
\I The One who loved us and cleansed us.
\BI \I Rev 1:5 \Q{To Him who loved us and washed us from our sins 
                in His own blood, \ldots} \EI
\I The Crucified and Risen Savior.
\BI \I Rev 1:18 \Q{I am He who lives, and was dead, and behold, 
                    I am alive forevermore.} 
    \I Rev 5:6 \Q{And I looked, and behold, in the midst of the throne
                    and of the four living creatures, and in the midst of the
                    elders, stood a Lamb as though it had been slain, \ldots}
    \I Rev 13:8 \Q{All who dwell on the earth will worship him [the beast], 
                    whose names have not been written in the Book of Life
                    of the Lamb who was slain from the foundation of the world.}
                    \EI
\I Worthy of worship.
\BI \I Rev 5:9 \Q{``You are worthy to take the scroll, \\
                    And to open its seals; \\
                    For You were slain, \\
                    And have redeemed us to God by Your blood \\
                    Out of every tribe and tongue and people and nation, \ldots''}
    \I Rev 5:12 \Q{``Worthy is the Lamb who was slain \\
                    To receive power and riches and wisdom, \\
                    And strength and honor and glory and blessing!''}
    \I Rev 5:13 \Q{``Blessing and honor and glory and power \\
                    Be to Him who sits on the throne, \\
                    And to the Lamb, forever and ever!''} \EI
\I Promised Messiah from the line of David.
\BI \I Rev 5:5 \Q{``Do not weep. Behold, the Lion of the tribe of Judah,
                    the Root of David, has prevailed to open the scroll 
                    and to loose its seven seals.''}
    \I Rev 3:7 \Q{``He who has the key of David, He who opens and no one shuts, 
                    and shuts and no one opens.''}
    \I Rev 1:18 \Q{``And I have the keys of Hades and of Death.''} \EI
\I Final Salvation.
\BI \I Rev 19:7 \Q{``Let us be glad and rejoice and give Him glory,
                    for the marriage of the Lamb has come,
                    and His wife has made herself ready.''}
    \I Rev 7:17 \Q{``for the Lamb who is in the midst of the throne 
                    will shepherd them and lead them to living fountains of waters.
                    And God will wipe away every tear from their eyes.''}
    \I Rev 21:22-23 \Q{But I saw no temple in it, for the Lord God Almighty 
                    and the Lamb are its temple. The city had no need 
                    of the sun or of the moon to shine in it, 
                    for the glory of God illuminated it. The Lamb is its light.}
    \I Rev 22:1-2 \Q{And he showed me a pure river of water of life, 
                    clear as crystal, proceeding from the throne of God 
                    and of the Lamb. In the middle of its street, and on either
                    of the river, was the tree of life, which bore twelve fruits,
                    each tree yielding its fruit every month. 
                    The leaves of the tree were for the healing of the nations.}
    \I Rev 22:3-4 \Q{And there shall be no more curse, but the throne of God
                    and of the Lamb shall be in it, and His servants shall 
                    serve Him. They shall see His face, and His name shall be on
                    their foreheads.} \EI

\subsection{He is the conquering King}
\I No longer clothed in humility, but He comes with power to avenge.
\BI \I Rev 1:7 \Q{Behold, He is coming with clouds, and every eye will see Him, 
                even they who pierced Him. And all the tribes of the earth
                will mourn because of Him. Even so, Amen.}
    \I Rev 1:14-16 \Q{His head and hair were white like wool, as white as snow,
                and His eyes like a flame of fire; His feet were like brass, 
                as if refined in a furnace, and His voice as the sound of 
                many waters; He had in his right hand seven stars, 
                out of His mouth went a sharp two-edged sword, 
                and His countenance was like the sun shining in its strength.}
                \EI
\I He comes with great wrath.
\BI \I Rev 6:16-17 \Q{\ldots and said to the mountains and rocks, 
                ``Fall on us and hide us from the face of Him who sits on the
                throne and from the wrath of the Lamb! For the great day of His
                wrath has come, and who is able to stand?''}
    \I Rev 14:14 \Q{Then I looked, and behold, a white cloud, and on the cloud
                sat One like the Son of Man, having on His head a golden crown, 
                and in His hand a sharp sickle.} \EI
\I He will be victorious.
\BI \I Rev 17:14 \Q{``These [ten kings and the beast] will make war with 
                the Lamb, 
                and the Lamb will overcome them, for He is Lord of lords and
                King of kings; and those who are with Him are called, 
                chosen, and faithful.''}
    \I Rev 19:11-16 \Q{Now I saw heaven opened, and behold, a white horse.
                And He who sat on Him was called Faithful and True,
                and in righteousness He judges and makes war.
                His eyes were like a flame of fire, and on His head were
                many crowns. He had a name written that no one knew except
                Himself. He was clothed with a robe dipped with blood,
                and His name is called The Word of God.
                And the armies of heaven, clothed in fine linen, white and
                clean, followed Him on white horses.
                Now out of His mouth goes a sharp sword, that with it He 
                should strike the nations. And He Himself will rule them 
                with a rod of iron. He Himself treads the winepress of the
                fierceness and wrath of Almighty God. And He has on His robe 
                and on His thigh a name written:
                \Q{KING OF KINGS \\ AND LORD OF LORDS.}} \EI

\I He is the final Judge.
\BI \I Rev 20:15 \Q{And anyone not found written in the Book of Life was cast 
                into the lake of fire.}
            Note: we know this is the Lamb's Book of Life from Rev 13:8. \EI

\subsection{Application}
\I We need to know who Jesus is.
\BI \I Knowing His sovereignty will give us peace.
    \I Knowing His salvation will produce love and devotion to Him.
    \I Knowing His eternal reward will keep us from pursuing the things of
        the world.
    \I Knowing His victory will give us courage unto obedience. \EI

@@

\subsection{Things which must shortly take place}
\I \emph{Transition:} We must make Revelation an urgent, \#1 priority,
    because it informs us of the imminent.
\I If imminent back then, how much more so now!
\I Revelation has \emph{not} been fulfilled:
\BI \I We are not in the new heaven and the new earth.
    \I Death and Hades have not been thrown into the lake of fire.
    \I Sin has not been abolished.
    \I There still remains the final battle against Satan and the world.
    \I The final judgement of sinners and the righteous.
    \I Christ's evaluation of believers. \EI
\I These things are future, but not far off, they are future imminent.
\BI \I The Lord is not slow, He is merciful (2 Peter 3:19)
    \I Nothing is hard for Him, 
        but His judgement would have been far too much for you to bear! \EI
\I The Second Coming is unheralded, it comes without warning.
\BI \I Rev 22:7, 12 \Q{``Behold! I am coming quickly!''}
    \I Rev 16:15 \Q{``Behold! I am coming as a thief''} \EI
\I We must learn from the flood of Noah's time (Matt 24:38-39).
    \Q{``For as in the days before the flood, they were eating and drinking,
    marrying and giving in marriage, until the day that Noah entered
    the ark, and did not know until the flood came and took them all away,
    so also will the coming of the Son of Man be.''} 
\I We must be those who are prepared for His return 
    (Matt 25, parable of the virgins).
\I And we can start on this by reading, understanding, and obeying
    the Revelation of Jesus Christ.
\EI
\end{document}
